What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-06 icpc/icpc2010.tex
comparing maxdb and mysql

We observed that MySQL had more topic subsets than MaxDB. MySQL 3.23 also had more topics and a longer recorded history than MaxDB 7.500. We tagged more MySQL topics with annotations than MaxDB topics yet both shared similarities. In terms of non-functional requirements both projects had long running trends that focused on functionality, maintainability, and portability, yet MaxDB had more of a focus on efficiency and reliability. We feel that MaxDB differed from MySQL because MaxDB was being actively developed where was by half way through our history of MySQL 3.23, other versions of MySQL were being actively developed: MySQL versions 4.0 and 4.1 and eventually 5.0 and 5.1. MySQL 3.23 was being maintained rather than actively developed where as MaxDB 7.500 was being actively developed into MaxDB 7.6, and then maintained thereafter.

MySQL and MaxDB's machine learners did dispatch off of some shared words. Words that were used to classify topics that were shared between MySQL and MaxDB included: bug, code, compiler, database, HP UX, delete, memory, missing, problems, removed, add, added, changed, problem, and test. Potentially adding these words to the word bags of \textsf{exp2} and \textsf{exp3} could improve performance while still being domain specific.

>>>>

We observed that MySQL had more topic subsets than MaxDB. MySQL 3.23 also had more topics and a longer recorded history than MaxDB 7.500. We tagged more MySQL topics with annotations than MaxDB topics yet both shared similarities. In terms of non-functional requirements both projects had long running trends that focused on functionality, maintainability, and portability, yet MaxDB had more of a focus on efficiency and reliability. We feel that MaxDB differed from MySQL because MaxDB was being actively developed where was by half way through our history of MySQL 3.23, other versions of MySQL were being actively developed: MySQL versions 4.0, 4.1, and eventually 5.0 and 5.1. MySQL 3.23 was being maintained rather than actively developed where as MaxDB 7.500 was being actively developed into MaxDB 7.6, and then maintained thereafter.

MySQL and MaxDB's machine learners did make decisions based off some shared words. Words that were used to classify topics that were shared between MySQL and MaxDB included: bug, code, compiler, database, HP UX, delete, memory, missing, problems, removed, add, added, changed, problem, and test. Adding these words to the word bags of \textsf{exp2} and \textsf{exp3} could improve performance while ensuring they were only domain specific.
